\textbf{Carlos Costa} born at Paços de Ferreira, Portual, 1991, is a M.Eng. student at Faculty of Engineering of University of Porto and a researcher at Centre for Robotics and Intelligent Systems in InescTec. His main research areas are localization and mapping of autonomous vehicles along with computer vision, safety critical systems and augmented reality.

\textbf{Héber Sobreira} Heber Sobreira born in  Leiria, Portugal, July, 1985, graduated with a M.Sc. degree in Electrical Engineering from the University of Porto in 2009. Since then, he has been developing his research within the Robotic and Intelligent Systems Unit of INESC-Porto (the Institute for Systems and Computer Engineering of Porto). His main research area is navigation and control of indoor autonomous vehicles.

\textbf{Armando Sousa} received his PhD at the Faculty of Engineering of the University of Porto (FEUP), Portugal, in 2004 in the field of robotics. His current research interests include Robotics and Automation, mainly in the data fusion and robotic perception field. He is currently a professor at FEUP and is also very interested in the Educational area namely in the technical field. He is also currently a researcher in InescTec. He participated largely in the RoboCup Federation Robotic Soccer Leagues where he won several "European" titles and was vice-champion of the world in 2006 in the Small Size League.

\textbf{Germano Veiga} received his PhD in 2009 at the Faculty of Engineering of the University of Coimbra, Portugal, in the field of Industrial robotics. He is currently leading the research projects at the Centre for Robotics and Intelligent Systems at InescTec. His research interests are spread among robotics, computer vision, networking and human-machine interfaces.
